Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-01-17 paper/paper.tex
kappa, etc

\begin{figure}[tb]
    \setlength{\abovecaptionskip}{0pt}
    \input{gen-graph-non-induced.tex}
    \caption{Behaviour of algorithms on the non-induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern edge probability and the y-axis is the target
        edge probability, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions, and the black lines are our
        predictions of where the phase transition will occur. On the second row, we show the number
    of search nodes used by the Glasgow algorithm, on the third row, the number of search nodes used
by the LAD algorithm, and the fourth, VF2; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

\begin{figure*}[tb]
    \setlength{\abovecaptionskip}{0pt}
    \input{gen-graph-induced.tex}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The second, third and fourth rows show the number of search nodes used by the
    Glasgow, LAD and VF2 algorithms. The fifth row shows a bound on the satisfiable region, by
    considering where a \emph{non-}induced isomorphism may also be a non-induced isomorphism between
    complement graphs. The final row shows when the Glasgow algorithm performs better when given the
    complements of the pattern and target graphs as inputs. ?? Also plot constrainedness
here.}\label{figure:induced}
\end{figure*}

@@

?? Constrainedness predicts the hard region in the middle \citep{Gent:1996:Kappa}! Add a two line
description of kappa, the slightly modified way we calculated it, and plot it on the graph.

>>>>

\begin{figure}[tb]
    \setlength{\abovecaptionskip}{0pt}
    \input{gen-graph-non-induced.tex}
    \caption{Behaviour of algorithms on the non-induced variant. For each plot, the x-axis is the
        pattern edge probability and the y-axis is the target edge probability, both from 0 to 1.
        Along the top row, we show the proportion of instances which are satisfiable; the white
        bands shows the phase transitions, and the black lines are our predictions of where the
        phase transition will occur. On the second row, we show the number of search nodes used by the
        Glasgow algorithm, on the third row, the number of search nodes used by the LAD algorithm, and the
        fourth, VF2; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

\begin{figure*}[p]
    \input{gen-graph-induced.tex}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The second, third and fourth rows show the number of search nodes used by the
    Glasgow, LAD and VF2 algorithms. The fifth row shows a bound on the satisfiable region, by
    considering where a \emph{non-}induced isomorphism may also be a non-induced isomorphism between
    complement graphs. The sixth row plots constrainedness: the darkest region is where
    constrainedness is exactly one, and the lighter regions show where the problem is either over-
    or under-constrained. The final row shows when the Glasgow algorithm performs better when given
    the complements of the pattern and target graphs as
inputs.}\label{figure:induced}
\end{figure*}

@@

?? Constrainedness predicts the hard region in the middle \citep{Gent:1996:Kappa}! Add a two line
description of kappa, the slightly modified way we calculated it. We plot this on the sixth row of
\cref{figure:induced}.
